Twists of supersymmetric gauge theories

### 2019-08-29 paper.tex
Fixing clashes

\tikzstyle{s16} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=red!30]
\tikzstyle{s16chiral} = [s16, dashed]
\tikzstyle{s8 } = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=orange!30]
\tikzstyle{s4} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=yellow!30]
\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=green!30]
\tikzstyle{dimension} = [circle, text centered, text width=0.7cm, minimum height=0.7cm, draw=black]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

We call $\cE$ the {\em space of BV fields}.  
The pairing $\omega$ equips the algebra of local functionals on $E$ with a shifted bracket, in the following way.
In Section 3 of \cite{CosRenorm}, it is shown that to every {\em local} functional $f \in \cO(\cE)$ there exists a symplectic vector field $X_f$ on $\cE$ whose Hamiltonian function is $f$. 
Note that if $f$ is degree $n$, then $X_f$ is of degree $n+1$ due to the degree of $\omega$.

\begin{definition}
The {\bf BV antibracket} $\{-,-\}$ is the bilinear map of cohomological degree $+1$
\[
\{-,-\} : \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE)
\]
defined by sending a pair $(f,g)$ to the local functional $X_f (g)$.
\chris{Also cite \cite{WittenAntibracket}.}
\end{definition}

This pairing is graded symmetric and satisfies the graded Jacobi identity.
Note that since local functionals do not form an algebra, it is not a (shifted) Poisson bracket.

@@

When we dimensionally reduce the minimally twisted 10- or 9-dimensional super Yang-Mills theories to 8 dimensions we obtain either the twist by a supercharge of type 1, or of type 3, depending on whether we reduce along an invariant direction or a non-invariant direction. \chris{I should say this more clearly, maybe including some general discussion at the beginning of the section, and referring to the figure.}

\subsubsection{The Holomorphic and Topological Twists}
Square-zero supercharges in the 10d $\mc N=(1,0)$ supersymmetry algebra correspond to holomorphic supercharges in the 8d $\mc N=1$ supersymmetry algebra.  As such, we can calculate the holomorphic twist of 8d $\mc N=1$ super Yang-Mills by dimensionally reducing the holomorphic twist of 10d $\mc N=(1,0)$ super Yang-Mills along a copy of $\CC$.  This theory can, however, be made canonically $\ZZ$-graded.

On the other hand, the topological twist -- the twist by an impure Weyl spinor -- of 8d $\mc N=1$ super Yang-Mills theory does not arise by dimensionally reducing a twisted theory in 9 dimensions.  This will be our first example of an A-type twist, as we discussed in Section \ref{A_twist_section} \chris{to add}: we will understand it as a family of degenerations of the holomorphic twist -- the twist by a pure Weyl spinor.

The holomorphic supercharge is stabilized by the group $\SU(4)$, and the topological supercharge is stabilized by $\spin(7)$.  If we want to stabilize the full one-parameter family describing the degeneration, we have to decompose our fields according to the action of the intersection $\SU(4) \cap \spin(7) \iso \SU(3)$.  The BRST fields decompose as
\begin{align*}
A &\mapsto A_{0,1} + A_{1,0} + \chi^0_1 + \chi^0_2 \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg\\
\lambda_+ &\mapsto \psi^+_{0,1} + \psi^+_{1,0} + \chi^+_1 + \chi^+_2 \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg\\
\lambda_- &\mapsto \psi^-_{0,1} + \psi^-_{1,0} + \chi^-_1 + \chi^-_2 \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg
\end{align*}
along with the ghost and the two scalar fields $\phi_1$ and $\phi_2$, which remain unchanged.  In terms of these component fields we can write the BV action functional -- split into its BRST and antifield parts -- as
\begin{align*}
S_{\mr{BRST}} &= \\ 
S_{\mr{anti}} &= .
\end{align*}

\chris{There might be a clever trick to avoid these calculations, involving the 10d calculation we already did to argue that certain fields definitely don't contribute (the ones that died in the 10d holomorphic twist, so we're left with only $A_{0,1}, \chi^0_1, \phi_1, \psi^+_{0,1}, \psi^+_{1,0}, \psi^-_{0,1}$ and $\chi^-_1$.) -- I need to think about it.}

>>>>

\tikzstyle{s16} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=red!30]
\tikzstyle{s16chiral} = [s16, dashed]
\tikzstyle{s8} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=orange!30]
\tikzstyle{s4} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=yellow!30]
\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=green!30]
\tikzstyle{dimension} = [circle, text centered, text width=0.7cm, minimum height=0.7cm, draw=black]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

We call $\cE$ the {\bf space of BV fields}.  The pairing $\omega$ equips the algebra of local functionals on $E$ with a shifted Poisson bracket, in the following way.
\begin{definition}
The \emph{BV antibracket} $\{-,-\}$ is the \chris{give at least an informal definition and a reference to a formal definition in the book \cite{Book2}.  Also cite \cite{WittenAntibracket}.}
\end{definition}

@@

When we dimensionally reduce the minimally twisted 10- or 9-dimensional super Yang-Mills theories to 8 dimensions we obtain either the twist by a supercharge of type 1, or of type 3, depending on whether we reduce along an invariant direction or a non-invariant direction, as indicated on the ``8d'' row of Figure \ref{fig:superchargeorbits}.  The topological twist (type 2 in the list above) appears in the right-most column of the figure, and is not obtained by dimensional reduction from higher dimensions.

\subsubsection{The Holomorphic and Topological Twists}
Square-zero supercharges in the 10d $\mc N=(1,0)$ supersymmetry algebra correspond to holomorphic supercharges in the 8d $\mc N=1$ supersymmetry algebra.  As such, we can calculate the holomorphic twist of 8d $\mc N=1$ super Yang-Mills by dimensionally reducing the holomorphic twist of 10d $\mc N=(1,0)$ super Yang-Mills along a copy of $\CC$.  This theory can, unlike its 10- and 9-dimensional analogues, be made canonically $\ZZ$-graded.

On the other hand, the topological twist -- the twist by an impure Weyl spinor -- of 8d $\mc N=1$ super Yang-Mills theory does not arise by dimensionally reducing a twisted theory in 9 dimensions.  This will be our first example of an A-type twist, as we discussed in Section \ref{A_twist_section} \chris{to add}: we will understand it as a one parameter family of supercharges, degenerating at zero to the holomorphic twist -- the twist by a pure Weyl spinor.

The holomorphic supercharge is stabilized by the group $\SU(4)$, and the topological supercharge is stabilized by $\spin(7)$.  If we want to stabilize the full one-parameter family describing the degeneration, we have to decompose our fields according to the action of the intersection $\SU(4) \cap \spin(7) \iso \SU(3)$.  The BRST fields decompose as
\begin{align*}
A &\mapsto A_{0,1} + A_{1,0} + \chi^0_1 + \chi^0_2 \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg\\
\lambda_+ &\mapsto \psi^+_{0,1} + \psi^+_{1,0} + \chi^+_1 + \chi^+_2 \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg\\
\lambda_- &\mapsto \psi^-_{0,1} + \psi^-_{1,0} + \chi^-_1 + \chi^-_2 \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg
\end{align*}
along with the ghost $c$ and the two scalar fields $\phi_1$ and $\phi_2$, which remain unchanged.  In terms of these component fields we can write the action of our 1-parameter family of supercharges, which we'll denote by $Q_{\mr{hol}} + tQ'$.  We choose the two supercharge $Q_{\mr{hol}}$ and $Q'$ to each be pure individually, but to have impure sum.  The action of such a supercharge can be written in terms of a quadratic and a cubic interaction as
\begin{align*}
I^{(1)}_t &= \\
I^{(2)}_t &= .
\end{align*}

We can also write the BV action functional -- split into its BRST and antifield parts -- as
\begin{align*}
S_{\mr{BRST}} &= \\ 
S_{\mr{anti}} &= .
\end{align*}

\chris{There might be a clever trick to avoid these action functional calculations, involving the 10d calculation we already did to argue that certain fields definitely don't contribute (the ones that died in the 10d holomorphic twist, so we're left with only $A_{0,1}, \chi^0_1, \phi_1, \psi^+_{0,1}, \psi^+_{1,0}, \psi^-_{1,0}$ and $\chi^-_1$.) -- I need to think about it.}
